---
title: "Final Project Phase 1"
author: "Shane Hauck"
date: "2023-12-09"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)
```

```{r echo = FALSE}
library(tidyverse)
library(gridExtra)
library(GGally)
theme_set(theme_bw())
library(ggpubr)
```


```{r echo = FALSE}
vietnam <- read_csv("data/vietnam-health.csv")
vietnam <- vietnam %>%
  filter(ReaExam == "volunteer") %>%
  filter(RecExam != "unknow") %>%
  filter(RecPerExam != "unknow")
```


In a survey pertaining to Vietnamese propensity to attend periodic general health examinations, outreach efforts targeted 2,479 individuals, with 409 opting not to participate. The subsequent analysis focused on 2,070 valid observations, excluding two invalid responses and resulting in a final sample size of 2,068. Notably, one in every six individuals declined the invitation to participate. Interviews, lasting an average of 12–15 minutes, featured a diverse group of participants encompassing both genders and spanning ages 13 to 83 years. Females constituted 64.08% (1,340/2,068) of the participants, with an average age of 29.17 years. A significant portion (60%) fell within the 18 to 30-year age bracket. The majority had undergone their most recent General Health Examination (GHE) within the past year. Among respondents, 57.35% were married, and 54.35% held stable employment.

# Question 1

The Assistant Minister of Health is seeking to understand the factors influencing individuals' decisions to undergo annual health exams, aiming to devise effective strategies to increase participation. The provided summaries offer insights into various aspects of the information received during check-ups and the performance of healthcare professionals. 

The attractiveness of information falls within a range of 1 to 5, with a mean rating of 2.691, suggesting room for improvement. Similarly, the impressiveness of information received has a mean rating of 2.818, indicating a moderate level of satisfaction. Sufficiency of information, with a mean rating of 3.013, suggests that there is room for enhancement in providing comprehensive details. Ratings for the popularity of information and variables such as assurance, reliability, and empathy range from 2.798 to 3.695, highlighting areas where the healthcare system could be strengthened. These findings imply that addressing concerns related to the perceived value of check-ups, emphasizing affordability, and enhancing the expertise and empathy of healthcare providers could be pivotal in encouraging more individuals to undergo annual health exams. Further exploration into why people might be hesitant to engage in check-ups could guide targeted policy changes and communication strategies to address specific concerns and ultimately increase participation rates.

```{r echo = FALSE}
grid.arrange(
  ggplot(vietnam, aes(x = AttractInfo)) +
    geom_histogram(stat = "density"),
  ggplot(vietnam, aes(x = SuffInfo)) +
    geom_histogram(stat = "density"),
  ggplot(vietnam, aes(x = ImpressInfo)) +
    geom_histogram(stat = "density"),
  ggplot(vietnam, aes(x = PopularInfo)) +
    geom_histogram(stat = "density"),
  ggplot(vietnam, aes(x = Assurance)) +
    geom_histogram(stat = "density"),
  ggplot(vietnam, aes(x = Reliability)) +
    geom_histogram(stat = "density"),
  ggplot(vietnam, aes(x = Empathy)) +
    geom_histogram(stat = "density"),
  ncol = 4, nrow = 2
)
```

```{r}
pairs <- vietnam %>% select(AttractInfo, SuffInfo, ImpressInfo, PopularInfo, Assurance, Reliability, Empathy)
ggpairs(pairs)
```



# Question 2

**Population of Interest:**

In our investigation of the factors influencing individuals' decisions to forego annual health exams, a targeted exploration is essential. We narrow our focus to a specific subgroup—patients who have abstained from check-ups for over 12 months. This subgroup represents a distinctive cohort with prolonged intervals between health examinations, providing an invaluable lens through which to identify and understand the barriers and concerns that deter regular attendance. By examining this population, we aim to unveil insights that are crucial for tailoring interventions and strategies to address their unique needs and encourage more timely health check-ups.

```{r echo = FALSE}
vietnam <- vietnam %>%
  mutate(greaterthan12 = case_when(
    RecPerExam %in% c("b1224", "g24") ~ "yes",
    TRUE ~ RecPerExam
  )) %>%
  mutate(Insurance = ifelse(HealthIns == "yes" | ComSubsidy == "yes", "yes", "no")) %>%
  mutate(Waste = ifelse(Wsttime == "yes" | Wstmon == "yes", "yes", "no")) %>%
  mutate(
    HealthImp = case_when(
      NotImp == "yes" ~ "no",
      Habit == "yes" ~ "yes",
      HthyPriority == "yes" ~ "yes",
      FlwHealth == "yes" ~ "yes",
      FALSE ~ "no"
    ),
    HealthImp = ifelse(is.na(HealthImp), "unknown", HealthImp)
  )
corrcheck <- vietnam %>% ungroup() %>% select(HealthImp, NotImp, Habit, HthyPriority, FlwHealth)





```

**Covariates to Examine:**

To capture the multifaceted dynamics of decision-making in this context, we conduct a thorough examination of various covariates. Our analysis encompasses variables that reflect the perceived quality of healthcare information, including attractiveness, sufficiency, impressiveness, and popularity (AttractInfo, SuffInfo, ImpressInfo, PopularInfo). Additionally, we delve into factors associated with the interpersonal aspects of healthcare, such as assurance, reliability, and empathy. The socio-economic dimension is not overlooked, with considerations like Insurance, Waste, and Health Importance (HealthImp) integrated into our exploration. This holistic approach ensures that we leave no stone unturned, providing a comprehensive understanding of the determinants influencing prolonged intervals between health examinations.

```{r echo = FALSE}
# Calculate proportions for each variable

proportions_AttractInfo <- vietnam %>%
  mutate(AttractInfo = floor(AttractInfo)) %>%
  group_by(AttractInfo) %>%
  summarize(Proportion = sum(greaterthan12 == "yes") / n())


proportions_SuffInfo <- vietnam %>%
  mutate(SuffInfo = floor(SuffInfo)) %>%
  group_by(SuffInfo) %>%
  summarize(Proportion = sum(greaterthan12 == "yes") / n())

proportions_ImpressInfo <- vietnam %>%
  mutate(ImpressInfo = floor(ImpressInfo)) %>%
  group_by(ImpressInfo) %>%
  summarize(Proportion = sum(greaterthan12 == "yes") / n())

proportions_PopularInfo <- vietnam %>%
  mutate(PopularInfo = floor(PopularInfo)) %>%
  group_by(PopularInfo) %>%
  summarize(Proportion = sum(greaterthan12 == "yes") / n())

proportions_Assurance <- vietnam %>%
  mutate(Assurance = floor(Assurance)) %>%
  group_by(Assurance) %>%
  summarize(Proportion = sum(greaterthan12 == "yes") / n())

proportions_Reliability <- vietnam %>%
  mutate(Reliability = floor(Reliability)) %>%
  group_by(Reliability) %>%
  summarize(Proportion = sum(greaterthan12 == "yes") / n())

proportions_Empathy <- vietnam %>%
  mutate(Empathy = floor(Empathy)) %>%
  group_by(Empathy) %>%
  summarize(Proportion = sum(greaterthan12 == "yes") / n())

proportions_insurance <- vietnam %>%
  group_by(Insurance) %>%
  summarize(Proportion = sum(greaterthan12 == "yes") / n())


proportions_waste <- vietnam %>%
  group_by(Waste) %>%
  summarize(Proportion = sum(greaterthan12 == "yes") / n())

proportions_health_imp <- vietnam %>%
  group_by(HealthImp) %>%
  summarize(Proportion = sum(greaterthan12 == "yes") / n())

proportions_disc_disease <- vietnam %>%
  group_by(DiscDisease) %>%
  summarize(Proportion = sum(greaterthan12 == "yes") / n())

proportions_lessbelqual <- vietnam %>%
  group_by(Lessbelqual) %>%
  summarize(Proportion = sum(greaterthan12 == "yes") / n())

ggarrange(
  ggplot(proportions_AttractInfo, aes(x = AttractInfo, y = Proportion, fill = AttractInfo)) +
    geom_col(position = "dodge") +
    labs(title = "Attractiveness", x = "vietnam", y = "Proportion of Greater than 12 months", fill = "Rating"),
  ggplot(proportions_SuffInfo, aes(x = SuffInfo, y = Proportion, fill = SuffInfo)) +
    geom_col(position = "dodge") +
    labs(title = "Sufficiency", x = "vietnam", y = "Proportion of Greater than 12 months", ),
  ggplot(proportions_ImpressInfo, aes(x = ImpressInfo, y = Proportion, fill = ImpressInfo)) +
    geom_col(position = "dodge") +
    labs(title = "Impressiveness", x = "vietnam", y = "Proportion of Greater than 12 months", ),
  ggplot(proportions_PopularInfo, aes(x = PopularInfo, y = Proportion, fill = PopularInfo)) +
    geom_col(position = "dodge") +
    labs(title = "Popularity", x = "vietnam", y = "Proportion of People where its been Greater than 12 months", ),
  ggplot(proportions_Assurance, aes(x = Assurance, y = Proportion, fill = Assurance)) +
    geom_col(position = "dodge") +
    labs(title = "Assurance", x = "vietnam", y = "Proportion of Greater than 12 months", ),
  ggplot(proportions_Reliability, aes(x = Reliability, y = Proportion, fill = Reliability)) +
    geom_col(position = "dodge") +
    labs(title = "Reliability", x = "vietnam", y = "Proportion of Greater than 12 months", ),
  ggplot(proportions_Empathy, aes(x = Empathy, y = Proportion, fill = Empathy)) +
    geom_col(position = "dodge") +
    labs(title = "Empathy", x = "vietnam", y = "Proportion of Greater than 12 months", ),
  common.legend = TRUE, legend = "bottom", ncol = 4, nrow = 2
)

ggarrange(
  ggplot(proportions_insurance, aes(x = Insurance, y = Proportion, fill = Insurance)) +
    geom_col(position = "dodge") +
    labs(title = "Will Insurance Pay?", x = "vietnam", y = "Proportion of Greater than 12 months", fill = "Rating"),
  ggplot(proportions_waste, aes(x = Waste, y = Proportion, fill = Waste)) +
    geom_col(position = "dodge") +
    labs(title = "Is it a Waste?", x = "vietnam", y = "Proportion of Greater than 12 months"),
  ggplot(
    proportions_health_imp %>% filter(HealthImp != "unknown"),
    aes(x = HealthImp, y = Proportion, fill = HealthImp)
  ) +
    geom_col(position = "dodge") +
    labs(title = "Is Health Important?", x = "vietnam", y = "Proportion of Greater than 12 months"),
  ggplot(proportions_disc_disease, aes(x = DiscDisease, y = Proportion, fill = DiscDisease)) +
    geom_col(position = "dodge") +
    labs(title = "Fear of Discovery of Disease", x = "vietnam", y = "Proportion of Greater than 12 months"),
  ggplot(proportions_lessbelqual, aes(x = Lessbelqual, y = Proportion, fill = Lessbelqual)) +
    geom_col(position = "dodge") +
    labs(title = "Little Faith in quality of medical service?", x = "vietnam", y = "Proportion of Greater than 12 months"),
  common.legend = TRUE, legend = "bottom", ncol = 3, nrow = 2
)
```

By employing a range of bar plots to illuminate the distribution of each variable within the group surpassing the 12-month checkup interval. The EDA enhances our grasp of the unique characteristics inherent in this specific subgroup, laying the groundwork for further analysis.

Further Analysis: 

* Standardize continuous predictors across all variables to enable a direct and meaningful comparison. By assessing the absolute values of standardized coefficients, we identify and prioritize the most influential factors contributing to the decision to avoid regular health examinations.

* Calculate the change in R-squared for each variable when introduced last to the model. The variables associated with the most substantial increase in R-squared signify their unique explanatory power within the context of prolonged intervals between health examinations.

By employing these analytical approaches, our aim is not only to uncover the driving forces behind individuals' decisions to avoid annual health exams but also to inform targeted strategies and interventions that address the specific needs of this subgroup. This meticulous investigation ensures a nuanced and tailored approach to promoting more frequent and timely health check-ups within the identified population of interest.

# Question 3


**Population of Interest:**
To address the Deputy Assistant Minister's hypothesis effectively, the population of interest should be individuals who have abstained from check-ups for over 12 months. Within this group, we need to distinguish between those who have health issues or have family members with health issues and those who do not.

```{r echo = FALSE}
proportions_PerTrmt <- vietnam %>%
  group_by(PerTrmt) %>%
  summarize(Proportion = sum(greaterthan12 == "yes") / n())

proportions_AcqTrmt <- vietnam %>%
  group_by(AcqTrmt) %>%
  summarize(Proportion = sum(greaterthan12 == "yes") / n())

proportions_StabHthStt <- vietnam %>%
  group_by(StabHthStt) %>%
  summarize(Proportion = sum(greaterthan12 == "yes") / n())

proportions_MedCabinet <- vietnam %>%
  group_by(MedCabinet) %>%
  summarize(Proportion = sum(greaterthan12 == "yes") / n())

proportions_ExamTools <- vietnam %>%
  group_by(ExamTools) %>%
  summarize(Proportion = sum(greaterthan12 == "yes") / n())

proportions_EvalExer <- vietnam %>%
  group_by(EvalExer) %>%
  summarize(Proportion = sum(greaterthan12 == "yes") / n())

proportions_Age_gr <- vietnam %>%
  group_by(Age_gr) %>%
  summarize(Proportion = sum(greaterthan12 == "yes") / n())
```


In alignment with the Deputy Assistant Minister's hypothesis, our analytical focus centers on covariates susceptible to influence from health issues or family health history. The variables under scrutiny include Perceived Treatment (PerTrmt), gauging individuals' perceptions of medical treatment efficacy; Acquaintance with Family Member Receiving Treatment (AcqTrmt), examining whether respondents have family members undergoing medical treatment; Stable Health Status (StabHthStt), assessing the stability of respondents' health status; Medicine Cabinet (MedCabinet), indicating preparedness and access to basic healthcare necessities at home; Examination Tools (ExamTools), exploring the availability of tools for self-examination; Exercise Evaluation (EvalExer), evaluating individuals' exercise habits; and Age Group (Age_gr), categorizing respondents based on age for insights into generational differences. This comprehensive set of covariates provides a nuanced exploration into the intricate interplay of personal health experiences, familial influences, lifestyle choices, and age-related factors that collectively contribute to individuals' decisions regarding the frequency of health check-ups.

```{r echo = FALSE}
ggarrange(
  ggplot(proportions_PerTrmt, aes(x = PerTrmt, y = Proportion, fill = PerTrmt)) +
    geom_col(position = "dodge") +
    labs(title = "Perceived Treatment", x = "vietnam", y = "Proportion of Greater than 12 months", fill = "Rating"),
  ggplot(proportions_AcqTrmt, aes(x = AcqTrmt, y = Proportion, fill = AcqTrmt)) +
    geom_col(position = "dodge") +
    labs(title = "Family Member Receiving Treatment", x = "vietnam", y = "Proportion of Greater than 12 months"),
  ggplot(proportions_StabHthStt, aes(x = StabHthStt, y = Proportion, fill = StabHthStt)) +
    geom_col(position = "dodge") +
    labs(title = "Stable Health Status", x = "vietnam", y = "Proportion of Greater than 12 months"),
  ggplot(proportions_MedCabinet, aes(x = MedCabinet, y = Proportion, fill = MedCabinet)) +
    geom_col(position = "dodge") +
    labs(title = "Medicine Cabinet", x = "vietnam", y = "Proportion of Greater than 12 months"),
  ggplot(proportions_ExamTools, aes(x = ExamTools, y = Proportion, fill = ExamTools)) +
    geom_col(position = "dodge") +
    labs(title = "Examination Tools", x = "vietnam", y = "Proportion of Greater than 12 months"),
  ncol = 4, nrow = 2, common.legend = TRUE, legend = "bottom"
)

ggplot(proportions_EvalExer, aes(x = EvalExer, y = Proportion, fill = EvalExer)) +
  geom_col(position = "dodge") +
  labs(title = "Exercise Evaluation", x = "vietnam", y = "Proportion of Greater than 12 months")

ggplot(proportions_Age_gr, aes(x = Age_gr, y = Proportion, fill = Age_gr)) +
  geom_col(position = "dodge") +
  labs(title = "Age Group", x = "vietnam", y = "Proportion of Greater than 12 months")
```

Analysis Approach:

Univariate Analysis: Start by examining each covariate individually to understand its distribution within the group that has exceeded the 12-month checkup interval. This provides a preliminary overview of potential associations.

Multivariate Analysis: Perform multivariate analysis by considering all relevant covariates together. This approach allows us to identify interactions and assess the combined impact of multiple factors on the probability of getting a check-up.

Quantifying Effects: Utilize logistic regression to quantify the effects of each covariate on the probability of getting a check-up. The odds ratio can be a useful measure to communicate the impact, indicating how the odds of getting a check-up change with each unit increase in the covariate.

Comparing Effects: Compare the odds ratios of different covariates to determine their relative importance in influencing the probability of getting a check-up. This comparison helps in identifying the most impactful factors.

The formal analysis should involve a combination of univariate and multivariate approaches, employing logistic regression to quantify the effects. The odds ratio becomes a key metric for communication, allowing a straightforward comparison of the influence of different covariates. By systematically examining these factors, we can provide valuable insights into whether health issues or family health history significantly impact individuals' decisions to undergo regular health check-ups.


```{r}
vietnam <- vietnam %>%
  mutate(howlong = ifelse(greaterthan12 == "yes", 1, 0)) %>%
  filter(HealthImp != "unknown") 
```

```{r}
vietnam <- vietnam %>%
  group_by(id, date) %>%
  mutate(
    perceptionMean = sum(AttractInfo + SuffInfo + ImpressInfo + PopularInfo)/4,
    compassionMean = sum(Assurance + Reliability + Empathy)/3
  )
```

```{r}
mod1 <- lm(howlong ~ perceptionMean + compassionMean + Age_gr + Insurance + Waste + HealthImp + DiscDisease + Lessbelqual, data = vietnam)
summary(mod1)
```

