---
title: "Final Project"
author: "Vinay Maruri"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(tidyverse)
```
#PART 1

#SHANE THIS IS WHERE I GOT MY PLOTS/STUFF I USED FOR PART 1

```{r}
vh <- read.csv("vietnam-health.csv")
```

Question 1

```{r}
#suffinfo, attractinfo, popularinfo, impressinfo
q1 <- vh[, 44:47]
summary(q1)
```

```{r}
tbl <- psych::describe(q1)
tbl <- tbl[, c(2:5, 8:9)]
rownames(tbl) <- c("Sufficiency", "Attractiveness", "Impressiveness", "Popularity")
colnames(tbl) <- c("N", "Mean", "Standard Deviation", "Median", "Minimum", "Maximum")
```

```{r}
q12 <- vh[, c(34, 36, 37)]
summary(q12)
tbl2 <- psych::describe(q12)
tbl2 <- tbl2[, c(2:5, 8:9)]
colnames(tbl2) <- c("N", "Mean", "Standard Deviation", "Median", "Minimum", "Maximum")
```

QUESTION 2

```{r}
defined <- subset(vh, RecPerExam != "unknow")
```


```{r}
tmp <- defined %>% group_by(RecPerExam, HealthIns) %>% count()
```



```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = HealthIns)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, Sex) %>% count()
```



```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = Sex)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, Jobstt) %>% count()
```



```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = Jobstt)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, MaritalStt) %>% count()
```



```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = MaritalStt)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, Edu) %>% count()
```



```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = Edu)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, place) %>% count()
```



```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = place)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, ReaExam) %>% count()
```



```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = ReaExam)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, Wsttime) %>% count()
```



```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = Wsttime)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, Wstmon) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = Wstmon)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, DiscDisease) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = DiscDisease)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, Lessbelqual) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = Lessbelqual)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, NotImp) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = NotImp)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, HthyPriority) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = HthyPriority)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, ComSubsidy) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = ComSubsidy)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, Habit) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = Habit)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, FlwHealth) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = FlwHealth)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, PerTrmt) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = PerTrmt)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, AcqTrmt) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = AcqTrmt)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = StabHthStt)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, MedCabinet) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = MedCabinet)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, Tooluseskills) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = Tooluseskills)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, ExpCare) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = ExpCare)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, ExamTools) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = ExamTools)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, UseMon) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = UseMon)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, StChoise) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = StChoise)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, CHPerc) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = CHPerc)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, SuitFreq) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = SuitFreq)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, AffCost) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = AffCost)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, UseIT) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = UseIT)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, AfterIT) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = AfterIT)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, EvalExer) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, fill = EvalExer)) + geom_col()
```



```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, HealthIns) %>% count()
```



```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = HealthIns)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, Sex) %>% count()
```



```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = Sex)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, Jobstt) %>% count()
```



```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = Jobstt)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, MaritalStt) %>% count()
```



```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = MaritalStt)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, Edu) %>% count()
```



```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = Edu)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, place) %>% count()
```



```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = place)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, ReaExam) %>% count()
```



```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = ReaExam)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, Wsttime) %>% count()
```



```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = Wsttime)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, Wstmon) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = Wstmon)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, DiscDisease) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = DiscDisease)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, Lessbelqual) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = Lessbelqual)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, NotImp) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = NotImp)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, HthyPriority) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = HthyPriority)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, ComSubsidy) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = ComSubsidy)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, Habit) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = Habit)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, FlwHealth) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = FlwHealth)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, PerTrmt) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = PerTrmt)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, AcqTrmt) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = AcqTrmt)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = StabHthStt)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, MedCabinet) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = MedCabinet)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, Tooluseskills) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = Tooluseskills)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, ExpCare) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = ExpCare)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, ExamTools) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = ExamTools)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, UseMon) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = UseMon)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, StChoise) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = StChoise)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, CHPerc) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = CHPerc)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, SuitFreq) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = SuitFreq)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, AffCost) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = AffCost)) + geom_col()
```

```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, UseIT) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = UseIT)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, AfterIT) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = AfterIT)) + geom_col()
```


```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, EvalExer) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = EvalExer)) + geom_col()
```



```{r}
tmp <- defined %>% group_by(RecPerExam, StabHthStt, EvalExer) %>% count()
```


```{r}
ggplot(tmp, aes(x = RecPerExam, y = n, col = StabHthStt, fill = EvalExer)) + geom_col()
```



#EDA: note missing values and values that will be dropped


```{r}
vietnam <- read_csv("~/linear_models/final/vietnam-health.csv")
viet_missing <- vietnam %>%
  filter(RecExam != "unknow") %>%
  filter(RecPerExam != "unknow") %>% 
  filter(SuitExer != "unknown") %>% 
  filter(CHPerc != "unknown")
```

```{r}
vietnam2 <- vietnam %>%
  filter(RecExam == "unknow" | RecPerExam == "unknow" | SuitExer == "unknown" | CHPerc == "unknown")
```


#PART 2

#SHANE THIS IS WHERE MY PART 3 STUFF IS

Analysis Approach:

Univariate Analysis: Start by examining each covariate individually to understand its distribution within the group that has exceeded the 12-month checkup interval. This provides a preliminary overview of potential associations.

Multivariate Analysis: Perform multivariate analysis by considering all relevant covariates together. This approach allows us to identify interactions and assess the combined impact of multiple factors on the probability of getting a check-up.

Quantifying Effects: Utilize logistic regression to quantify the effects of each covariate on the probability of getting a check-up. The odds ratio can be a useful measure to communicate the impact, indicating how the odds of getting a check-up change with each unit increase in the covariate.

Comparing Effects: Compare the odds ratios of different covariates to determine their relative importance in influencing the probability of getting a check-up. This comparison helps in identifying the most impactful factors.

The formal analysis should involve a combination of univariate and multivariate approaches, employing logistic regression to quantify the effects. The odds ratio becomes a key metric for communication, allowing a straightforward comparison of the influence of different covariates. By systematically examining these factors, we can provide valuable insights into whether health issues or family health history significantly impact individuals' decisions to undergo regular health check-ups.


```{r}
vietnam <- vietnam %>%
  mutate(howlong = ifelse(greaterthan12 == "yes", 1, 0)) %>%
  filter(HealthImp != "unknown") 
```

```{r}
vietnam <- vietnam %>%
  group_by(id, date) %>%
  mutate(
    perceptionMean = sum(AttractInfo + SuffInfo + ImpressInfo + PopularInfo)/4,
    compassionMean = sum(Assurance + Reliability + Empathy)/3
  )
```

```{r}
mod1 <- lm(howlong ~ perceptionMean + compassionMean + Age_gr + Insurance + Waste + HealthImp + DiscDisease + Lessbelqual, data = vietnam)
summary(mod1)
```

```{r}
full_model <- glm(howlong ~ Age + Sex + Jobstt + MaritalStt + Edu + height + weight + place + BMI + HealthIns + Wsttime + Wstmon + DiscDisease + ComSubsidy + Habit + FlwHealth + PerTrmt + AcqTrmt + StabHthStt + MedCabinet + Tooluseskills + ExpCare + ExamTools + UseMon + Tangibles + Reliability + Respon + Assurance + Empathy + StChoise + CHPerc + SuitFreq + AffCost + UseIT + AfterIT + SuffInfo + AttractInfo + ImpressInfo + PopularInfo + SuitExer + EvalExer + Age_gr, data = vietnam, family = "binomial")
summary(full_model)
```
#interactions of stable health status:

```{r}
interaction.plot(x.factor = vietnam$perceptionMean, 
                 trace.factor = vietnam$StabHthStt, 
                 response = vietnam$howlong)
```


```{r}
interaction.plot(x.factor = vietnam$compassionMean, 
                 trace.factor = vietnam$StabHthStt, 
                 response = vietnam$howlong)
```

```{r}
summary(aov(howlong ~ perceptionMean*StabHthStt, data = vietnam))
```
```{r}
summary(aov(howlong ~ perceptionMean*StabHthStt, data = vietnam))
```

```{r}
summary(aov(howlong ~ Age_gr*StabHthStt, data = vietnam))
```

```{r}
summary(aov(howlong ~ HealthImp*StabHthStt, data = vietnam))
```

poly(perceptionmean, 4) bs(compassionmean, knots = c(2, 3, 4)) stabhthstthealthimp waste insurance lessbelqual sex age_gr 

```{r}
summary(aov(howlong ~ perceptionMean + compassionMean + StabHthStt + HealthImp + Waste + Insurance + Lessbelqual + Sex + Age_gr + StabHthStt*compassionMean, data = vietnam))
```


```{r}
summary(aov(howlong ~ perceptionMean + compassionMean + StabHthStt + HealthImp + Waste + Insurance + Lessbelqual + Sex + Age_gr + StabHthStt*perceptionMean, data = vietnam))
```

```{r}
model = glm(howlong ~ perceptionMean + compassionMean + StabHthStt + HealthImp + Waste + Insurance + Lessbelqual + Sex + Age_gr + StabHthStt*compassionMean + StabHthStt*perceptionMean, data = vietnam, family = binomial(link = "logit"))
summary(model)
```


```{r}
model = glm(howlong ~ perceptionMean + compassionMean + StabHthStt + HealthImp + Waste + Insurance + Lessbelqual + Sex + Age_gr + StabHthStt*compassionMean + StabHthStt*perceptionMean, data = vietnam, family = binomial(link = "logit"))
summary(model)
```

```{r}
model = glm(howlong ~ perceptionMean + compassionMean + StabHthStt + StabHthStt*compassionMean + StabHthStt*perceptionMean, data = vietnam, family = binomial(link = "logit"))
summary(model)
```


